Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/paper.Rmd
change sentence so it becomes clear that range is an additional argument

The "Spatial blocking" from package \pkg{blockCV} comes with various blocking options such as random (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`).
However, instead of using these options, the user might also supply a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) which will create a quadratic block pattern across the study area.
<!--JM: to stay consistent please add the argument which lets the user indicate a user-defined polygon-->
This kind of blocking might be of special interest for SDM studies as well as the possibility to supply a user-defined polygon with predefined blocking zones.

>>>>

The "Spatial blocking" from package \pkg{blockCV} comes with various blocking options such as random (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`).
Additionally, the user might supply a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) which will ensure a quadratic block pattern across the study area.
<!--JM: to stay consistent please add the argument which lets the user indicate a user-defined polygon-->
This kind of blocking might be of special interest for SDM studies as well as the possibility to supply a user-defined polygon with predefined blocking zones.
